Supplementary Material for `The response of trophic interaction networks to multiple stressors in a marine latitudinal gradient of the Southern Hemisphere'

### 2024-03-27 manuscript.Rmd
Ms corrections

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
bibliography: JAE_Review.bib
csl: "environmental-reviews.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

@@

The most common stressor reported along the southwest Atlantic - Antarctic gradient is global warming, except for Beagle Channel and Burdwood Bank, which are more influenced by the introduction of an alien species and fisheries, respectively (section 3, Table 3). The main characteristics of global warming in the region, and the most plausible drivers of change, are: sea warming, glacial retreat, elevated sediment input in the water column, and reduction of the sea ice extent. These drivers act in different ways and magnitudes in the studied locations along the latitudinal gradient. 
Despite emphasizing global warming in this section, this does not mean that no other stressors act or interact with global warming in the study systems, potentially buffering the overall effect on the food web (e.g. sea warming and fishery in San Jorge Gulf).
Climate change has led to several well-documented impacts on marine species regarding distributional shifts induced by warming of marine currents [@Poloczanska2013; @Wu2012; @Verges2019]. Furthermore, warmer temperatures increase species metabolic rates [@Brown2004]. Changes in metabolic rates can subsequently translate into shifts in species traits (body size, @Vucic-Pestic2011; @Klein2018], biomass [@Perry2020] and distribution [@Kortsch2015]. Alterations in the species body size and distributions have ripple effects on feeding interactions, for example, it can introduce new feeding interactions [@Pecuchet2020; @Verges2014], modify existing ones, and shorten energy pathways [@Bartley2019; @OGorman2019], and reduce trophic efficiencies [@Vucic-Pestic2011].

>>>>

---
output:
  pdf_document:
    latex_engine: xelatex
    keep_tex: yes
  word_document: default
bibliography: JAE_Review.bib
csl: "environmental-reviews.csl"
documentclass: article
geometry:
- vmargin=1in
- hmargin=1in
header-includes:
- \usepackage{pdflscape,booktabs}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage[running]{lineno}
- \linenumbers
---

@@

The most common stressor reported along the southwest Atlantic - Antarctic gradient is global warming, except for Beagle Channel and Burdwood Bank, which are more influenced by the introduction of an alien species and fisheries, respectively (section 3, Table 3). The main characteristics of global warming in the region, and the most plausible drivers of change, are: sea warming, glacial retreat, elevated sediment input in the water column, and reduction of the sea ice extent. These drivers act in different ways and magnitudes in the studied locations along the latitudinal gradient. 
Despite emphasizing global warming in this section, this does not mean that no other stressors act or interact with global warming in the study systems, potentially buffering the overall effect on the food web (e.g. sea warming and fishery in San Jorge Gulf).
Climate change has led to several well-documented impacts on marine species regarding distributional shifts induced by warming of marine currents [@Poloczanska2013; @Wu2012; @Verges2019]. Furthermore, warmer temperatures increase species metabolic rates [@Brown2004]. Changes in metabolic rates can subsequently translate into shifts in species traits (e.g. body size, @Vucic-Pestic2011; @Klein2018), biomass [@Perry2020], and distribution [@Kortsch2015]. Alterations in the species body size and distributions have ripple effects on feeding interactions, for example, it can introduce new feeding interactions [@Pecuchet2020; @Verges2014], modify existing ones, and shorten energy pathways [@Bartley2019; @OGorman2019], and reduce trophic efficiencies [@Vucic-Pestic2011].
